### 2013-07-02 gapoly.Rmd
included markdowns for 2 dataset tests

```{r}
n.vars     <- 3  # x1, x2,... 
max.compts <- 4  # poly = compt1 + compt2 + ...
max.degree <- 3
```

@@

Eg: consider polynomial $x_1^2 \times x_3 + x_3^3 + x_1 \times x_2$

@@

```{r}
make.component <- function(bits, n.vars) {
  vars <- paste0("x",1:n.vars)
  elements <- split(bits, ceiling(seq_along(bits)/(length(bits)/n.vars)))
  str <- ""
  for(i in 1:length(elements)) {
    power <- length(elements[[i]][elements[[i]]==1])
    if (power == 1)
      if (str=="")
        str = vars[i]
      else  
        str = paste0(str, "*", vars[i])
    if (power > 1)
      if (str=="")
        str = paste0(vars[i], "^", power)
      else  
        str = paste0(str, "*", vars[i], "^", power)
  }
  str
}

@@

Let's check the previous eg, $x_1^2 \times x_3 + x_3^3 + x_1 \times x_2$:

>>>>

```{r}
n.vars     <- 3  # x1, x2,... 
max.compts <- 4  # poly = compt1 + compt2 + ...
max.degree <- 3  # meaning exponents up to 2^max.degree - 1
```

@@

Eg: consider polynomial $x_1^3 \times x_3 + x_3^7 + x_1 \times x_2$

@@

```{r}
bin2dec <- function(x) 
    sum(2^(which(rev(unlist(strsplit(as.character(x), "")) == 1))-1))

make.component <- function(bits, n.vars) {
  vars <- paste0("x",1:n.vars)
  elements <- split(bits, ceiling(seq_along(bits)/(length(bits)/n.vars)))
  str <- ""
  for(i in 1:length(elements)) {
    # power <- length(elements[[i]][elements[[i]]==1]) previous coding
    power <- bin2dec(elements[[i]])
    if (power == 1)
      if (str=="")
        str = vars[i]
      else  
        str = paste0(str, "*", vars[i])
    if (power > 1)
      if (str=="")
        str = paste0(vars[i], "^", power)
      else  
        str = paste0(str, "*", vars[i], "^", power)
  }
  str
}

@@

Let's check the previous eg, $x_1^3 \times x_3 + x_3^7 + x_1 \times x_2$:

### 2013-07-02 tests_test.Rmd
included markdowns for 2 dataset tests

```{r, message = FALSE, tidy = FALSE, echo = F}
## knitr configuration: http://yihui.name/knitr/options#chunk_options
opts_chunk$set(comment = "", error= TRUE, warning = FALSE, message = FALSE,
               tidy = FALSE, cache = TRUE, echo = T,
               fig.width = 6, fig.height = 6)
```
Testing Ailerons
========================================================

```{r}
source("gapolyfuncs.R")

set.seed(101)

@@

filename <- "Ailerons/ailerons"  # where is the data (under dataset folder)
filepath <- paste0("datasets/",filename)
my.data <- read.csv(filepath)

@@

my.data <- na.omit(my.data) # the dataset has some NAs
my.data <- my.data[,c(1:25,27:41)] # x26 is almost all zeros

@@

sapply(my.data, class)
my.data$x1 <- as.numeric(my.data$x1) # x1 was a factor, make it a numeric value
head(my.data,8)

@@

source("gapolyfuncs.R")
report <- make.report(my.data, population=200, iterations=200)

@@

df <- data.frame(ga.poly = report$ga.error, 
                 lin.reg = report$lm.error,
                 svm = report$svm.error,
                 rpart = report$rpart.error,
                 rf = report$rf.error,
                 ci.tree = report$citree.error)

save(report, file="Ailerons.Rda") # recover with load("Ailerons.Rda")

write.table(df, "Ailerons.txt")

@@

Tabela para Ailerons dataset
------

>>>>

```{r, message = FALSE, tidy = FALSE, echo = F}
## knitr configuration: http://yihui.name/knitr/options#chunk_options
opts_chunk$set(comment = "", error= TRUE, warning = FALSE, message = FALSE,
               tidy = FALSE, cache = TRUE, echo = T,
               fig.width = 6, fig.height = 6)
```
Testing Test

========================================================

```{r}
set.seed(101)

@@

size <- 50
my.data <- data.frame(x1 <- rpois(size,4),
                      x2 <- rnorm(size),
                      y <- x1*x2 + x1)

@@

@@

sapply(my.data, class)
my.data$x1 <- as.numeric(my.data$x1) # x1 becomes a numeric value
head(my.data,8)

@@

source("gapolyfuncs.R")
report <- make.report(my.data, population=20, iterations=20)

@@

@@
